State of the Practice for Medical Imaging Software

### 2022-03-28 StateOfPractice/Papers/MedImageSoft_SOP-arXiv/MedImageSoft_SOP_AcademicRadiology.tex
Revisions to Section 5 (Comparison to community ranking)

Generally speaking, most of the top-ranking MI software projects also received
greater attention and popularity on GitHub. Between our ranking and the GitHub
stars-per-year ranking, four of the top five software projects are the same.
Any more stats?

In some cases projects are popular in the community, but our methodology ranked
them low.  This is the case for \textit{dwv}. The reason for the low ranking is
that, as mentioned in Section~\ref{sec_result_installability}, we failed to
build it locally, and used the test version on its websites for the
measurements. We followed the instructions and tried to run the command ``yarn
run test'' locally, which did not work. In addition, the test version did not
detect a broken DICOM file and displayed a blank image as described in
Section~\ref{sec_result_robustness}. We might underestimate the scores for
\textit{dwv} due to uncommon technical issues. We also ranked \textit{DICOM
Viewer} much lower than its popularity. As mentioned in
Section~\ref{sec_result_installability} it depended on the NextCloud platform
that we could not successfully install. Thus, we might underestimate the scores
of its surface reliability and surface robustness. In addition, we weighted all
qualities equally, which is not likely to be the case with all users. As a
result, some projects with high community popularity may have scored lower with
our method because of poor scores for some qualities.  A further explanation for
discrepancies between our measures and the star measures may also be due to
inaccuracy with using stars to approximate popularity.  Stars are not an idea
measure because stars represent the community's feeling in the past more than
current preferences \citep{Szulik2017}, since stars tend only to be added, not
removed.

\begingroup
\renewcommand{\arraystretch}{0.85}
\begin{table}[!ht]
\centering
\begin{tabular}{lllll}
\toprule
Software & Our ranking & Stars/yr & Watches/yr & Forks/yr \\ 
\midrule
3D Slicer & 1 & 284 & 19 & 128 \\
OHIF Viewer & 3 & 277 & 19 & 224 \\
dwv & 23 & 124 & 12 & 51 \\
ImageJ & 2 & 84 & 9 & 30 \\
ParaView & 5 & 67 & 7 & 28 \\
Horos & 12 & 49 & 9 & 18 \\
Papaya & 17 & 45 & 5 & 20 \\
Fiji & 4 & 44 & 5 & 21 \\
DICOM Viewer & 29 & 43 & 6 & 9 \\
INVESALIUS 3 & 10 & 40 & 4 & 17 \\
Weasis & 6 & 36 & 5 & 19 \\
dicompyler & 26 & 35 & 5 & 14 \\
OsiriX Lite & 9 & 34 & 9 & 24 \\
MRIcroGL & 18 & 24 & 3 & 3 \\
GATE & 25 & 19 & 6 & 26 \\
Ginkgo CADx & 14 & 19 & 4 & 6 \\
BioImage Suite Web & 8 & 18 & 5 & 7 \\
Drishti & 27 & 16 & 4 & 4 \\
Slice:Drop & 20 & 10 & 2 & 5 \\
ITK-SNAP & 15 & 9 & 1 & 4 \\
medInria & 7 & 7 & 3 & 6 \\
SMILI & 13 & 3 & 1 & 2 \\
MatrixUser & 28 & 2 & 0 & 0 \\
MicroView & 16 & 1 & 1 & 1 \\
Gwyddion & 11 & n/a & n/a & n/a \\
XMedCon & 19 & n/a & n/a & n/a \\
DicomBrower & 21 & n/a & n/a & n/a \\
AMIDE & 22 & n/a & n/a & n/a \\
3DimViewer & 24 & n/a & n/a & n/a \\ 
\bottomrule
\end{tabular}
\caption{Software ranking versus GitHub metrics (Sorted in descending order of
GitHub popularity, as estimated by the number of new stars per year)}
\label{tab_ranking_vs_GitHub}
\end{table}
\endgroup

>>>>

Generally speaking, most of the top-ranking MI software projects also received
greater attention and popularity on GitHub. Between our ranking and the GitHub
stars-per-year ranking, four of the top five software projects appear in both
lists.Our top 5 packages are scattered among the first 8 positions on the GitHub
list. However, as discussed below there are discrepancies between the two lists.

In some cases projects are popular in the community, but were assigned a low
rank by our methodology.  This is the case for \textit{dwv}. The reason for the
low ranking is that, as mentioned in Section~\ref{sec_result_installability}, we
failed to build it locally, and used the test version on its websites for the
measurements. We followed the instructions and tried to run the command ``yarn
run test'' locally, which did not work. In addition, the test version did not
detect a broken DICOM file and displayed a blank image as described in
Section~\ref{sec_result_robustness}. We might underestimate the scores for
\textit{dwv} due to uncommon technical issues. We also ranked \textit{DICOM
Viewer} much lower than its popularity. As mentioned in
Section~\ref{sec_result_installability} it depended on the NextCloud platform
that we could not successfully install. Thus, we might underestimate the scores
of its surface reliability and surface robustness. In addition, we weighted all
qualities equally, which is not likely to be the case with all users. As a
result, some projects with high community popularity may have scored lower with
our method because of a relatively higher (compared to the scientific
community's implicit ranking) weighting of the poor scores for some qualities. A
further explanation for discrepancies between our measures and the star measures
may also be due to inaccuracy with using stars to approximate popularity.  Stars
are not an ideal measure because stars represent the community's feeling in the
past more than they measure current preferences \citep{Szulik2017}.  The issue
with stars is that they tend only to be added, not removed.  A final reason for
inconsistencies between our ranking and the community's ranking is that, as for
consumer products, more factors influence popularity than just quality.

\begingroup
\renewcommand{\arraystretch}{0.85}
\begin{table}[!ht]
\centering
\begin{tabular}{llllll}
\toprule
Software & Comm.\ rank & Our rank & Stars/yr & Watches/yr & Forks/yr \\ 
\midrule
3D Slicer & 1 & 1 & 284 & 19 & 128 \\
OHIF Viewer & 2 & 3 & 277 & 19 & 224 \\
dwv & 3 & 23 & 124 & 12 & 51 \\
ImageJ & 4 & 2 & 84 & 9 & 30 \\
ParaView & 5 & 5 & 67 & 7 & 28 \\
Horos & 6 & 12 & 49 & 9 & 18 \\
Papaya & 7 & 17 & 45 & 5 & 20 \\
Fiji & 8 & 4 & 44 & 5 & 21 \\
DICOM Viewer & 9 & 29 & 43 & 6 & 9 \\
INVESALIUS 3 & 10 & 10 & 40 & 4 & 17 \\
Weasis & 11 & 6 & 36 & 5 & 19 \\
dicompyler & 12 & 26 & 35 & 5 & 14 \\
OsiriX Lite & 13 & 9 & 34 & 9 & 24 \\
MRIcroGL & 14 & 18 & 24 & 3 & 3 \\
GATE & 15 & 25 & 19 & 6 & 26 \\
Ginkgo CADx & 16 & 14 & 19 & 4 & 6 \\
BioImage Suite Web & 17 & 8 & 18 & 5 & 7 \\
Drishti & 18 & 27 & 16 & 4 & 4 \\
Slice:Drop & 19 & 20 & 10 & 2 & 5 \\
ITK-SNAP & 20 & 15 & 9 & 1 & 4 \\
medInria & 21 & 7 & 7 & 3 & 6 \\
SMILI & 22 & 13 & 3 & 1 & 2 \\
MatrixUser & 23 & 28 & 2 & 0 & 0 \\
MicroView & 24 & 16 & 1 & 1 & 1 \\
Gwyddion & 25 & 11 & n/a & n/a & n/a \\
XMedCon & 26 & 19 & n/a & n/a & n/a \\
DicomBrower & 27 & 21 & n/a & n/a & n/a \\
AMIDE & 28 & 22 & n/a & n/a & n/a \\
3DimViewer & 29 & 24 & n/a & n/a & n/a \\ 
\bottomrule
\end{tabular}
\caption{Software ranking by our methodology versus the community (Comm.)
ranking using GitHub metrics (Sorted in descending order of community
popularity, as estimated by the number of new stars per year)}
\label{tab_ranking_vs_GitHub}
\end{table}
\endgroup
